Icicle: write once, run once

### 2016-05-26 2016fhpc/section/04-Benchmarks.tex
update benchmarks

\begin{tikzpicture}
\begin{axis}[
	x tick label style={/pgf/number format/1000 sep=},
	ylabel=MB/s,
	enlargelimits=0.01,
	legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
	ybar interval=0.7,
  symbolic x coords={R, grep, wc, Icicle-372, wc -l, Icicle-1, disk, end}
]
\addplot coordinates {(R,6.6) (grep,74) (wc,251) (Icicle-372,543) (wc -l,775) (Icicle-1,1060) (disk,1800) (end,0) };

@@

\caption{Benchmark results}
\label{fig:bench:table}
\end{figure}

The table in figure~\ref{fig:bench:table} shows the throughput in megabytes per second.
We compared the throughput of several programs over the same 360GB dataset:
\begin{itemize}
\item our original R implementation (R);
\item Icicle with equivalent queries (Icicle-372);
\item Icicle with a single query computing the mean (Icicle-1);
\item finding empty lines with @grep "^$"@;
\item counting characters, words and lines with @wc@;
\item counting only lines with @wc -l@; and
\item the sequential read speed of the disk (@disk@).
\end{itemize}
All of the unix utilities were run with the collation set to @LANG=C@ for maximum performance.

>>>>

\begin{tikzpicture}
\begin{axis}[
	x tick label style={/pgf/number format/1000 sep=},
	ylabel=MB/s,
	enlargelimits=0.01,
	legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
	ybar interval=0.7,
  symbolic x coords={R, grep, wc, Icicle-372, wc -l, cat, Icicle-1, end}
]
\addplot coordinates {(R,6.0) (grep,74) (wc,182.6) (Icicle-372,846) (wc -l,852) (cat,878) (Icicle-1,1029) (end,0) };

@@

\caption{Throughput comparisons of Icicle against existing R code and standard unix utilities}
\label{fig:bench:other}
\end{figure}

\begin{tikzpicture}
\begin{axis}[
	x tick label style={/pgf/number format/1000 sep=},
	ylabel=MB/s,
  ymin=0, ymax=1100,
%  xmax=372,
  xlabel=Number of queries,
	enlargelimits=0.01,
	legend style={at={(0.5,-0.1)},anchor=north,legend columns=-1},
%	ybar interval=0.7,
]
\addplot coordinates {(0,1025.5) (1,1029.6) (48,978) (96,941) (144,943) (192,936) (240,904) (276,895.5) (324,881) (372,846.2) };

\caption{Decrease in throughput as queries are added}
\label{fig:bench:queries}
\end{figure}

The table in figure~\ref{fig:bench:other} shows the throughput in megabytes per second.
We compared the throughput of several programs over the same 360GB dataset:
\begin{itemize}
\item our original R implementation (R);
\item Icicle with equivalent queries (Icicle-372);
\item Icicle with a single query computing the mean (Icicle-1);
\item finding empty lines with @grep "^$"@;
\item counting characters, words and lines with @wc@;
\item counting only lines with @wc -l@; and
\item the sequential read speed of the disk (@disk@).
\end{itemize}
All of the unix utilities were run with the collation set to @LANG=C@ for maximum performance.
